### 2018-09-27 README.Rmd
update citation

        @article{hejazi2018methyvim,
          doi = {},
          url = {},
          year  = {2018},
          month = {},
          publisher = {},
          volume = {},
          author = {Hejazi, Nima S and Phillips, Rachael V and Hubbard, Alan E
            and {van der Laan}, Mark J},
          title = {methyvim: Targeted, Robust, and Model-free Differential
            Methylation Analysis in {R}},
          journal = {}
        }

>>>>

        @article{hejazi2018methyvim,
          doi = {10.12688/f1000research.16047.1},
          url = {https://dx.doi.org/10.12688/f1000research.16047.1},
          year = {2018},
          publisher = {Faculty of 1000 Ltd},
          volume = {7},
          number = {1424},
          author = {Hejazi, Nima S and Phillips, Rachael V and Hubbard, Alan E
            and {van der Laan}, Mark J},
          title = {{methyvim}: Targeted, robust, and model-free differential
            methylation analysis in {R}},
          journal = {F1000Research}
        }
